---
output: html_document
---

<style>

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  min-width: 50%;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

</style>

[![](`r if(dir.exists("images")) paste0(getwd(),"/") else ""`images/icon.png){width=15%}
![](`r if(dir.exists("images")) paste0(getwd(),"/") else ""`images/logo.png){width=50%}](https://sixtysixwards.com)

```{r setup0, include=FALSE, out.width='80%'}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)

# USE_MAPS <- TRUE
# ELECTION <- "20191105"
# CONFIG <- get_config(ELECTION)
# USE_LOG <- CONFIG$use_log

setwd("C:/Users/Jonathan Tannen/Dropbox/sixty_six/posts/election_night_needle/")
# source("needle.R")

if(ELECTION == "20191105"){
  file <- "raw_data/results_20191105_213752.csv"
} else {
  files <- list.files("raw_data", full.names = T)
  file <- max(files)
}

turnout_office <- "MAYOR"

df <- load_data(file)
current_time <- file.info(file)$mtime

pretty_time <- gsub("^0","", format(lubridate::ymd_hms(Sys.time()), "%I:%M"))

n_reporting <- length(unique(df$warddiv))
needle_params <- readRDS(sprintf("outputs/needleparams_%s_log%s_svd.Rds", ELECTION, USE_LOG))

if(CONFIG$is_primary){
  office_suffix <- function(x) paste0(x, "-DEM")
  turnout_svd <- needle_params@turnout_svds$dem
  n_council_winners <- 5
} else {
  office_suffix <- identity
  turnout_svd <- needle_params@turnout_svds$general
  n_council_winners <- 7
}
pvote_svd <- needle_params@pvote_svd

turnout_sim <- simulate_turnout(
  df=df, 
  turnout_office=office_suffix(turnout_office), 
  turnout_svd=turnout_svd, 
  verbose=FALSE
)
```

# Live Election Night Predictions
Updated at `r pretty_time`, with `r scales::comma(n_reporting)` out of `r scales::comma(nrow(divs))` precincts reporting.

**Disclosure**: This is an experimental project to project final results from incomplete returns. Read about [the ways it did well, and the ways it didn't](https://sixtysixwards.com/home/was-the-needle-omniscient-or-lucky/) in the primary. TLDR: I use historic correlations to predict the divisions that haven't reported yet, including uncertainty. If divisions correlate differently this year than they have in the past, this will be wrong. Of course, that usually doesn't happen.

### Council At Large
```{r council_at_large, fig.asp = 2.0, out.width="100%"}
## Since we have 3 columns and ceil(ncand/3) rows, 
## fig.asp should be ceil(ncand/3) / 3
simulate_office <- function(
  office, 
  office_name, 
  n_winners=1,
  consider_divs=NULL
){
  simulate_pvote(
    df,
    use_office=office_suffix(office),
    office_name=office_name,
    turnout_sim=turnout_sim,
    pvote_svd=pvote_svd,
    n_winners=n_winners,
    verbose=FALSE,
    consider_divs=consider_divs
  )
}

council_at_large_plot <- simulate_office(
  "COUNCIL AT LARGE",
  "Council At Large",
  n_winners=n_council_winners
)

council_at_large_plot[["needle"]] %>% print()
```

### Council District 10
```{r , fig.asp = 0.5, out.width="100%"}
get_council_divs <- function(district){
  divs_to_council$warddiv[
    divs_to_council$council == as.character(district)
  ]
}

add_suffix_to_num <- function(x){
  x <- as.character(x)
  last_digit <- substr(x, nchar(x), nchar(x))
  if(substr(x, nchar(x)-1, nchar(x)) %in% c(11,12,13)) return(paste0(x, "TH"))
  if(last_digit==1) return(paste0(x, "ST"))
  if(last_digit==2) return(paste0(x, "ND"))
  if(last_digit==3) return(paste0(x, "RD"))
  return(paste0(x, "TH"))
}

simulate_district <- function(district_num){
  office <- sprintf("DISTRICT COUNCIL-%s DISTRICT", add_suffix_to_num(district_num))
  simulate_office(
    office,
    office_name=sprintf("Council District %s", district_num),
    consider_divs = get_council_divs(district_num)
  )
}

district_10_plot <- simulate_district(10)

district_10_plot[["needle"]] %>% print()
```

### Mayor
```{r mayor, fig.asp = 0.33, out.width="100%"}
mayor_plot <- simulate_office("MAYOR", "Mayor")

mayor_plot[["needle"]] %>% print()
```

# Maps

### Council At Large
```{r council_at_large_map, fig.asp = 2.0, out.width="100%"}
council_at_large_plot[["map"]] %>% print()
```

### Council District 10
```{r district_10_map, fig.asp = 0.5, out.width="100%"}
district_10_plot[["map"]] %>% print()
```

### Mayor
```{r mayor_map, fig.asp = 0.5, out.width="100%"}
mayor_plot[["map"]] %>% print()
```

# Diagnostics

```{r diagnostics}
div_cats <- readRDS("../../data/processed_data/div_cats_2019-11-08.RDS")

pretty_simulated <- function(simulated) {
  ifelse(simulated, "Simulated Divisions", "Reporting Divisions")
}

turnout_sim %<>% mutate(simulated = pretty_simulated(simulated))

turnout_cat <- turnout_sim %>%
    left_join(div_cats %>% select(warddiv, cat)) %>%
    group_by(simulated, cat, sim) %>%
    summarise(
      n_divs = length(unique(warddiv)),
      turnout = sum(turnout)
    ) %>%
    gather(key="var", value="value", n_divs, turnout) %>%
    group_by(simulated, cat, var) %>%
    summarise(
      mean = mean(value),
      pct_975 = quantile(value, 0.975),
      pct_025 = quantile(value, 0.025)
    )

cat_colors <- c(
   "Black Voters" = light_blue, 
   "Wealthy Progressives" = light_red, 
   "White Moderates" = light_orange, 
   "Hispanic North Philly" = light_green
)

gg_turnout_cat <- ggplot(
  turnout_cat %>% mutate(key = ifelse(var=="turnout", "Turnout", "N(Divisions)")), 
  aes(x=cat, y=mean)
) + 
  geom_bar(stat="identity", aes(fill=cat)) +
  geom_errorbar(aes(ymin = pct_025, ymax=pct_975), width = 0.5) +
  facet_grid(key ~ simulated, scales="free_y") +
  theme_sixtysix() %+replace% theme(axis.text.x = element_blank()) +
  scale_y_continuous(labels=scales::comma) +
  scale_fill_manual(values=cat_colors) +
  labs(
    x=NULL,
    y=NULL,
    title="Turnout by Voting Bloc",
    fill=NULL
  )
print(gg_turnout_cat)
```

```{r candidate_sim_overall, out.width="100%", fig.asp=1}
gg_office_overall <- function(sim_list){
  cand_sim <- sim_list$office_sim %>%
    mutate(simulated = pretty_simulated(simulated)) %>%
    ## Doesn't account for different cands/voter
    left_join(turnout_sim %>% select(sim, warddiv, turnout)) %>%
    group_by(candidate, sim, simulated) %>%
    summarise(pvote = weighted.mean(pvote, w=turnout)) %>%
    group_by(candidate, simulated) %>%
    summarise(
      mean = mean(pvote),
      pct_975 = quantile(pvote, 0.975),
      pct_025 = quantile(pvote, 0.025)
    )
  
  cand_order <- sim_list$winners_sim %>% arrange(desc(pvote)) %>% with(candidate)
  cand_sim$candidate <- factor(cand_sim$candidate, levels = cand_order)
  
  ggplot(
    cand_sim, 
    aes(x=candidate, y=100*mean)
  ) + 
    geom_bar(stat="identity") +
    geom_errorbar(aes(ymin =100* pct_025, ymax=100*pct_975), width = 0.5) +
    geom_text(y = 0.4, aes(label = sprintf("%0.1f", 100*mean)), color="white") +
    facet_grid(simulated ~ .) +
    theme_sixtysix() %+replace% 
    theme(
      axis.text.x = element_text(angle=45, vjust = 0.8, hjust=0.8)
    ) +
    scale_y_continuous(labels=scales::comma) +
    labs(
      x=NULL,
      y="Percent of the vote",
      title="Simulated results",
      fill=NULL
    )
}

print(gg_office_overall(council_at_large_plot))
```

```{r office_cat, out.width="100%", fig.asp=5}
gg_office_cat <- function(sim_list){
  cand_sim_cat <- sim_list$office_sim %>%
    mutate(simulated = pretty_simulated(simulated)) %>%
    left_join(turnout_sim %>% select(sim, warddiv, turnout)) %>%
    left_join(div_cats %>% select(warddiv, cat)) %>%
    group_by(candidate, sim, cat, simulated) %>%
    summarise(pvote = weighted.mean(pvote, w=turnout)) %>%
    group_by(candidate, cat, simulated) %>%
    summarise(
      mean = mean(pvote),
      pct_975 = quantile(pvote, 0.975),
      pct_025 = quantile(pvote, 0.025)
    )
  
  cand_order <- sim_list$winners_sim %>% arrange(desc(pvote)) %>% with(candidate)
  cand_sim_cat$candidate <- factor(cand_sim_cat$candidate, levels = cand_order)
  
  ggplot(
    cand_sim_cat, 
    aes(x=cat, y=100*mean)
  ) + 
    geom_bar(stat="identity", aes(fill=cat)) +
    geom_errorbar(aes(ymin =100* pct_025, ymax=100*pct_975), width = 0.5) +
    facet_grid(candidate ~ simulated) +
    theme_sixtysix() %+replace% theme(axis.text.x = element_blank()) +
    scale_y_continuous(labels=scales::comma) +
    scale_fill_manual(values=cat_colors) +
    labs(
      x=NULL,
      y="Percent of the vote",
      title=sprintf("Needle Results as of %s pm", pretty_time),
      fill=NULL
    )
}

print(gg_office_cat(council_at_large_plot))

```
